\documentclass[11pt,a4paper]{article}

\usepackage[utf8]{inputenc}
\usepackage[T1]{fontenc}
\usepackage{amsmath,amssymb}
\usepackage{graphicx}
\usepackage{booktabs}
\usepackage{hyperref}
\usepackage[margin=0.9in]{geometry}
\usepackage{caption}
\usepackage{subcaption}
\usepackage{float}
\usepackage{xcolor}
\usepackage{longtable}
\usepackage{array}

\newcommand{\etg}{$E_T^\gamma$}
\newcommand{\pT}{$p_T$}
\newcommand{\isoET}{$E_T^{\rm iso}$}
\newcommand{\crit}[1]{\textcolor{red}{\textbf{#1}}}
\newcommand{\warn}[1]{\textcolor{orange}{\textbf{#1}}}
\newcommand{\info}[1]{\textcolor{blue}{#1}}
\newcommand{\ok}[1]{\textcolor{green!50!black}{\textbf{#1}}}

\title{Cross-Section Pipeline Cut--Efficiency Audit\\
\large Do all data-side cuts have a matching correction?}
\author{PPG12 Analysis Team (automated audit)}
\date{2026-04-21}

\begin{document}
\maketitle

\section*{Executive Summary}

A three-wave agent audit of the PPG12 isolated-photon cross-section
pipeline (\texttt{config\_bdt\_nom.yaml}, 1.5\,mrad and all-range)
was run to identify any selection cut applied to data that lacks a
corresponding efficiency correction. The cross-section formula is
\[
\frac{d^2\sigma}{dp_T\,d\eta}
= \frac{N_{\rm iso\,prompt}}{\mathcal{L}\cdot \varepsilon_{\rm reco}\cdot \varepsilon_{\rm iso}\cdot \varepsilon_{\rm id}\cdot \varepsilon_{\rm vtx+MBD}\cdot \Delta\eta\cdot \Delta p_T}\,,
\]
where $N_{\rm iso\,prompt}$ is the ABCD-subtracted, unfolded signal
yield.

\textbf{Primary findings.} Most cuts are properly absorbed --- the
common-block (NPB, $e_{11}/e_{33}$, $w_{r,{\rm cog}x}$,
$w_{\eta,{\rm cog}x}$), the tight shape/BDT block, the reco isolation,
the reco-vertex $|z|<60$\,cm cut, and the run/lumi weighting are all
accounted for in the $\varepsilon$ chain or absorbed by denominator
construction.

Three concerns:
\begin{enumerate}
  \item \crit{HIGH}\ --- \textbf{The Photon-4-GeV L1 trigger efficiency
  is not applied in the code.} The $\sim$99.1\% plateau is documented
  in the analysis note (\texttt{selection.tex:93}, \texttt{Figures/etc/Photon\_4\_GeV\_ConstantFit.pdf})
  but never injected into the yield. The factor conventionally named
  $\varepsilon_{\rm vtx+MBD}$ in the code
  (\texttt{CalculatePhotonYield.C:1031}, called \texttt{vertex\_eff\_val})
  corrects only the MBD N$\&$S coincidence $\times$ reco-vertex cut, not
  the EMCal-tower L1 threshold.
  \item \crit{HIGH}\ --- \textbf{Note-vs-code trigger-bit mismatch.}
  \texttt{config\_bdt\_nom.yaml:50} uses \texttt{trigger\_used: 30};
  \texttt{PPG12-analysis-note/selection.tex:93} states ``trigger bit
  26'' is used. Either these bits are aliases of the same physical
  Photon-4-GeV + MBD-NS trigger in two trigger maps, or one of the two
  is stale. This needs resolution before the note can be trusted on
  trigger content.
  \item \warn{WARN}\ --- \textbf{Latent pileup-veto ordering bug.} The
  \texttt{mbd\_avg\_sigma} veto at \texttt{RecoEffCalculator\_TTreeReader.C:1920--1927}
  is applied \emph{after} the truth-denominator histograms are filled
  (lines 1801--1830). Currently inactive in nominal and all on-disk
  configs (no config sets \texttt{mbd\_avg\_sigma\_max}), so current
  cross-section results are unaffected. But the code is a latent trap:
  any future pileup-metric systematic (the deleted
  \texttt{config\_bdt\_mbdrms\{01,03,05\}.yaml} family, or a fresh scan)
  would silently bias $\varepsilon_{\rm vtx+MBD}$.
\end{enumerate}

\noindent\textbf{Overall status.} The nominal cross-section is
internally consistent for every cut currently applied \emph{except} the
L1 Photon-4-GeV trigger plateau, which is an unjustified $\sim$1\%
under-correction on the yield. Impact on the central value:
the divisor \texttt{total\_eff} lacks the $\varepsilon_{\rm trig}
\approx 0.991$ factor, so the current \texttt{total\_eff} is
$1/0.991 \approx 1.009\times$ \emph{larger} than it should be, and the
cross-section $\sigma_{\rm code} = N_{\rm iso}/(\varepsilon_{\rm code}
\cdot\mathcal{L}\cdot\Delta\eta\cdot\Delta p_T)$ comes out
$\sim$0.9\% \emph{lower} than the correct
$\sigma_{\rm true} = \sigma_{\rm code}/\varepsilon_{\rm trig}$. In
other words: cross-section biased \emph{low} by $(1-\varepsilon_{\rm trig})
\approx 0.9\%$ above 10\,GeV, potentially larger in the 8--10\,GeV
underflow bin where the plateau is not yet reached.
Additionally, the systematic envelope advertised as ``MBD trigger
efficiency $\pm$5\%'' (\texttt{systematics.tex:129--137}, implemented via
\texttt{mbd\_eff\_scale}) covers the \emph{MBD side only} and does not
cover the missing EMCal-side plateau correction.

\medskip
\noindent\textbf{Scope.} This audit covers only \emph{selection cuts}
and their efficiency corrections. Out of scope: (i) cross-check of
signal-leakage corrections $c_B, c_C, c_D$ in the ABCD method (whether
the same tight/iso cuts applied on data also populate the MC-based
leakage templates); (ii) internal consistency of the RooUnfold response
matrix beyond the truth-fiducial mirror check
(\texttt{RecoEff:1620--1660, 2704} --- noted but not exercised);
(iii) luminosity-normalization correctness (the \texttt{trigger\_used:
30} vs note's ``bit 26'' is flagged under HIGH-2, but the 16.6 pb$^{-1}$
vs 48.93 pb$^{-1}$ choice between 1.5\,mrad and all-range per
\texttt{wiki/reference/constants-sync.md} is not re-audited here);
(iv) truth-vertex reweight (\texttt{truth\_vertex\_reweight\_on}) as a
per-event weight on MC, distinct from a cut-efficiency correction.

\section{Findings Table}

\begin{longtable}{@{}p{1.9cm}p{4.8cm}p{5.8cm}p{4.3cm}@{}}
\toprule
Severity & Location & Finding & Impact \\
\midrule
\crit{HIGH-1} &
\texttt{CalculatePhotonYield.C:1027--1038};
\texttt{config\_bdt\_nom.yaml:50};
\texttt{mbd\_trigger\_efficiency\_study.py} (unused output) &
No dedicated Photon-4-GeV L1 trigger efficiency is multiplied into
\texttt{total\_eff}. The only trigger-like factor is the offline
MBD-NS-coincidence $\times$ reco-vertex-cut ratio
(\texttt{vertex\_eff\_val}), which does not emulate the EMCal-tower
threshold. &
\etg-dependent $\sim$0.5--1\% under-correction on the cross-section
central value above 10\,GeV (per note plateau of 99.1\%). No
systematic currently envelopes the residual. \\
\addlinespace
\crit{HIGH-2} &
\texttt{config\_bdt\_nom.yaml:50} (\texttt{trigger\_used: 30}) vs
\texttt{PPG12-analysis-note/selection.tex:93} (``trigger bit 26'') &
Note and code disagree on the trigger bit used for Photon-4-GeV. Likely
reflects different trigger-bit \emph{maps} but needs explicit
confirmation; otherwise the lumi-list provenance (memory:
\texttt{Bit30Corr}) is loose. &
Analysis-note correctness. Either the bit-30 result is wrong and should
be bit-26, or the note needs updating. Lumi normalization may also be
implicated if maps differ in effective prescale. \\
\addlinespace
\warn{WARN-1} &
\texttt{RecoEffCalculator\_TTreeReader.C:1801--1830} (truth
histograms filled) vs \texttt{1920--1927} (MBD-$\sigma$ veto) &
Pileup veto ordered after the truth-denominator fill. Numerator
(reco side) would be cut; truth denominator would not. &
Latent only: no on-disk config activates the veto
(defaults to $\pm\infty$ via
\texttt{RecoEffCalculator\_TTreeReader.C:424--427}). Any future
\texttt{mbd\_avg\_sigma\_max} study resurrects the bias. \\
\addlinespace
\info{INFO-1} &
\texttt{config\_bdt\_nom.yaml:228--236} &
\texttt{common.e32\_over\_e35\_\{min,max\}} and
\texttt{common.et1\_\{min,max\}} are parsed but not referenced in
\texttt{passes\_common\_shape}. Dead fields. &
None. Source of future confusion; recommend deletion or wiring. \\
\addlinespace
\info{INFO-2} &
\texttt{CalculatePhotonYield.C:155}, 1031 (\texttt{mbd\_eff\_scale}) &
Nuisance knob nominally $=0$. In \texttt{make\_bdt\_variations.py:287}
the \texttt{mbd} systematic group is marked ``placeholder'' with no
concrete up/down variant configs on disk. &
The 5\% MBD-trigger systematic envelope in the note
(\texttt{systematics.tex:129--137}) is not yet wired into the pipeline
configs --- it is asserted, not computed, in the systematic-aggregation
step. \\
\addlinespace
\ok{PASS-1} &
\texttt{RecoEffCalculator\_TTreeReader.C:2704--2842} &
\ok{NPB preselection ($> 0.5$), $e_{11}/e_{33} < 0.98$,
$w_{r,{\rm cog}x} > 0$, $w_{\eta,{\rm cog}x} < 2$ are properly absorbed
into $\varepsilon_{\rm id}$} because the denominator is
$\{{\rm reco} \cap {\rm iso}\}$ without the common gate, while the
numerator carries the common gate (via \texttt{tight} requiring
\texttt{common\_pass}). Iso classification at line 2303 is
independent of the common gate; tight classification (line 2331) is
nested under it. & None. \\
\addlinespace
\ok{PASS-2} &
\texttt{config\_bdt\_nom.yaml:29, 47--48}; \texttt{RecoEffCalculator\_TTreeReader.C:1805, 1808, 1816} &
\ok{Reco-vertex $|z|<60$\,cm and parametric reco iso have matching
truth-level partners} (\texttt{vertex\_cut\_truth} defaults to
\texttt{vertex\_cut}; truth iso $<4$\,GeV fiducial). ABCD regions
cross-check consistent. & None. \\
\bottomrule
\end{longtable}

\section{Cut $\rightarrow$ Correction Mapping}

\begin{longtable}{@{}p{4.0cm}p{4.2cm}p{5.5cm}p{3.2cm}@{}}
\toprule
Cut (data side) & Where applied (file:line) & Correction / absorption mechanism & Status \\
\midrule
\endhead
\multicolumn{4}{l}{\textit{Event level}} \\
\midrule
Run range \texttt{[run\_min, run\_max]} &
\texttt{RecoEff:1501--1507} &
Lumi normalization (non-efficiency); MC prescaled via
\texttt{lumi\_weight = lumi / lumi\_target}. &
\ok{OK} \\
\addlinespace
Photon-4-GeV L1 trigger bit &
\texttt{RecoEff:1516--1535} (\texttt{trigger\_used: 30}) &
\textbf{Missing.} Only the MBD N$\&$S-coincidence piece is in
\texttt{vertex\_eff\_val}; the EMCal-tower L1 turn-on is not injected.
Note cites 99.1\% plateau. &
\crit{MISSING} \\
\addlinespace
Reco vertex $|z|<60$\,cm &
\texttt{RecoEff:1847--1867}; config \texttt{vertex\_cut: 60} &
$\varepsilon_{\rm vtx+MBD}
= h_{\rm truth\,pT,\,vtx+MBDcut} / h_{\rm truth\,pT,\,vtxcut}$,
with truth-side $|z_{\rm truth}|<\texttt{vertex\_cut\_truth}$ (=60
in nom). \texttt{CalcYield:1031}. &
\ok{OK} \\
\addlinespace
MBD N$\&$S coincidence (trigger component) &
\texttt{RecoEff:1816--1819} (MC truth-side numerator emulation) &
Same $\varepsilon_{\rm vtx+MBD}$ factor above. &
\ok{OK} (MBD side only) \\
\addlinespace
MBD $\sigma_t$ pileup veto &
\texttt{RecoEff:1920--1927} &
\textbf{Inactive in nominal} (no config sets the keys). If activated,
no correction mirrors the cut; ordering bug prevents absorption. &
\warn{LATENT} \\
\addlinespace
Trigger prescale weight (data) &
\texttt{RecoEff:1538--1554} &
Applied as per-event weight upscaling prescaled events (not an
efficiency). &
\ok{OK} \\
\midrule
\multicolumn{4}{l}{\textit{Cluster level -- kinematic acceptance}} \\
\midrule
$E_T > 5$\,GeV &
\texttt{RecoEff:1982--1983}; \texttt{CaloAna24.cc:1202} (=5 upstream) &
Response-matrix unfolding over \texttt{pT\_bins\_truth = [7,\ldots,45]}
absorbs reco-ET-threshold migration. &
\ok{OK} \\
\addlinespace
$|\eta_{\rm cluster}| \le 0.7$ &
\texttt{RecoEff:2159--2170}; config \texttt{eta\_bins: [-0.7, 0.7]} &
Truth side reuses the same \texttt{eta\_bins} array
(\texttt{RecoEff:1651, 1788}). No separate \texttt{eta\_bins\_truth}.
Fiducial $=$ reco. &
\ok{OK} \\
\midrule
\multicolumn{4}{l}{\textit{Cluster level -- isolation}} \\
\midrule
Reco iso parametric
$\isoET < b + s\cdot \etg$ &
\texttt{RecoEff:2300--2306} &
$\varepsilon_{\rm iso}$ at \texttt{CalcYield:1028} (ratio of
reco-iso-passed to reco-photon, denominator un-gated on common).
Truth-fiducial $\isoET^{\rm truth}<4$\,GeV absorbed by the
response-matrix truth axis. &
\ok{OK} \\
\midrule
\multicolumn{4}{l}{\textit{Cluster level -- shower-shape common cuts}} \\
\midrule
NPB $>0.5$ (when \texttt{common\_npb\_cut\_on=1}) &
\texttt{RecoEff:2320} &
Absorbed into $\varepsilon_{\rm id}$: denominator $=\{\rm reco\cap iso\}$
(no common gate); numerator $=\{\rm reco\cap iso\cap tight\cap common\}$. &
\ok{OK} \\
\addlinespace
$e_{11}/e_{33} \le 0.98$ &
\texttt{RecoEff:2313--2320} (\texttt{passes\_common\_shape}) &
Same mechanism as NPB $\rightarrow$ $\varepsilon_{\rm id}$. &
\ok{OK} \\
\addlinespace
$w_{r,{\rm cog}x} > 0$ &
\texttt{RecoEff:2313--2320} &
Same. &
\ok{OK} \\
\addlinespace
$w_{\eta,{\rm cog}x} < 2$ &
\texttt{RecoEff:2313--2320} &
Same. &
\ok{OK} \\
\addlinespace
\texttt{cluster\_prob} $\in [0, 1]$ &
\texttt{RecoEff:2313--2320} &
Trivially passed in nom; if activated, absorbed same as other common
cuts. &
\ok{OK} (inactive) \\
\midrule
\multicolumn{4}{l}{\textit{Cluster level -- tight signal block}} \\
\midrule
BDT tight parametric
$b_{\rm BDT} + s_{\rm BDT}\cdot \etg$ &
\texttt{RecoEff:2389--2404} &
Part of \texttt{tight}. $\varepsilon_{\rm id}$ absorbs. Systematic:
\texttt{tight\_bdt} variant $\rightarrow$ \texttt{eff} group. &
\ok{OK} \\
\addlinespace
10 shape variables in tight windows (\texttt{weta\_cogx}, \texttt{wphi\_cogx}, \texttt{et1--4}, \texttt{e11\_e33}, \texttt{e32\_e35}, \texttt{prob}) &
\texttt{RecoEff:2339--2407} &
Part of \texttt{tight} $\rightarrow$ $\varepsilon_{\rm id}$. &
\ok{OK} \\
\addlinespace
Non-tight anti-ID &
\texttt{RecoEff:2408--2507} &
Defines ABCD region C/D; pairs with \texttt{noniso} (config shift +0.8). &
\ok{OK} \\
\midrule
\multicolumn{4}{l}{\textit{Cluster level -- not actually used}} \\
\midrule
Saturated-tower veto (\texttt{nosat}) &
\texttt{RecoEff:1984--1988, 2012--2015} &
\texttt{nosat=0} in nom $\rightarrow$ inactive. &
\ok{OK} (inactive) \\
\addlinespace
\texttt{cluster\_mbd\_time\_min/max} &
\texttt{RecoEff:2207--2213} &
Keys not set in nom $\rightarrow$ inactive ($\pm 999$). \texttt{badtime}
flag never consumed downstream in A/B/C/D fill. &
\ok{OK} (inactive) \\
\addlinespace
$\chi^2$ cut on cluster &
Nowhere &
No such cut in the data path. &
\ok{N/A} \\
\addlinespace
$E_1/E_7$ cut &
Nowhere &
No such cut. Analysis does not use this shape variable. &
\ok{N/A} \\
\addlinespace
\texttt{common.e32\_over\_e35} /
\texttt{common.et1} &
Parsed at \texttt{config:228--236}, never referenced in \texttt{passes\_common\_shape} &
Dead fields. &
\info{INFO} \\
\midrule
\multicolumn{4}{l}{\textit{Upstream pre-selection}} \\
\midrule
\texttt{CaloAna24.cc:616} vertex $|v_z^{\rm MBD}|<200$\,cm &
DST writer (data only) &
Looser than the analysis $|z|<60$\,cm; no events lost in the analysis
range. &
\ok{OK} \\
\addlinespace
\texttt{CaloAna24.cc:1202} \texttt{clusterpTmin=5} GeV &
DST writer (both) &
Matches analysis $E_T > 5$\,GeV floor. Any tightening above 5 would
hit the preselection wall silently. &
\ok{OK} \\
\addlinespace
\texttt{CaloAna24.cc:464--467} bad-event blacklist (2 (run, evt) pairs) &
DST writer (both) &
Negligible effect on normalization; applied to data and MC identically. &
\ok{OK} \\
\addlinespace
\texttt{apply\_BDT.C} additional selection &
None (only adds BDT branches; \texttt{outtree->Fill()} unconditional) &
No new cuts introduced. &
\ok{OK} \\
\bottomrule
\end{longtable}

\section{Discussion of the HIGH-Severity Findings}

\subsection{HIGH-1: Photon-4-GeV L1 trigger efficiency not applied}

\paragraph{What the code does.} The only ``trigger'' efficiency factor
in \texttt{CalculatePhotonYield.C} is \texttt{vertex\_eff\_val} at lines
1031--1033:
\begin{verbatim}
  vertex_eff_val = h_truth_pT_vertexcut_mbd_cut->GetBinContent(ibin)
                 / h_truth_pT_vertexcut->GetBinContent(ibin)
                 + mbd_eff_scale;
\end{verbatim}
The numerator histogram is filled in
\texttt{RecoEffCalculator\_TTreeReader.C:1816--1819} on MC with the
requirement
\texttt{mbdnorthhit>=1 \&\& mbdsouthhit>=1 \&\& |vertexz|<vertexcut}. The
MBD-coincidence piece is the \emph{offline} N$\&$S N-hit requirement,
which emulates only the MBD side of the Photon-4-GeV + MBD-NS trigger.
The EMCal-tower side of the L1 bit (the 4\,GeV tower threshold and its
turn-on) is not emulated anywhere.

\paragraph{What the note says.} \texttt{PPG12-analysis-note/selection.tex:93}:
\begin{quote}
In this analysis, the ``Photon 4 GeV + MBD NS $\geq 1$'' trigger
(trigger bit 26) is used. This analysis reports photon \etg\ above
10 GeV (unfolding underflow bin starting from 8 GeV) where the trigger
efficiency is at a plateau about 99.1\%.
\end{quote}
A figure (\texttt{Figures/etc/Photon\_4\_GeV\_ConstantFit.pdf}) shows
the constant fit. The 0.991 value never appears in any \texttt{.C} or
\texttt{.py} or \texttt{.yaml} file in the pipeline.

\paragraph{Impact estimate.} The current code computes
$\sigma_{\rm code} = N_{\rm iso\,prompt}
/ (\varepsilon_{\rm code}\cdot\mathcal{L}\cdot\Delta)$, where
$\varepsilon_{\rm code} = \varepsilon_{\rm reco}\cdot
\varepsilon_{\rm iso}\cdot \varepsilon_{\rm id}\cdot
\varepsilon_{\rm vtx+MBD}$. The correct divisor is
$\varepsilon_{\rm true} = \varepsilon_{\rm code}\cdot
\varepsilon_{\rm trig}$, so the correct cross-section is
$\sigma_{\rm true} = \sigma_{\rm code}/\varepsilon_{\rm trig}$. With the
note's plateau $\varepsilon_{\rm trig} \approx 0.991$ for
$\etg \ge 10$\,GeV, $\sigma_{\rm code}$ is low by
$(1-0.991)/0.991 \approx 0.9\%$. In the underflow bin 8--10\,GeV the
plateau is not yet reached, so the bias is \etg-dependent and could
exceed a few percent there.

\paragraph{Adjacent issue: the 5\% systematic.}
\texttt{systematics.tex:129--137} assigns a ``MBD trigger efficiency''
systematic by varying \texttt{mbd\_eff\_scale}
(\texttt{CalculatePhotonYield.C:155}) by $\pm$5\%. This is a scaling
of the offline MBD-coincidence efficiency only --- it does not cover
the missing EMCal-tower plateau correction. Furthermore
\texttt{make\_bdt\_variations.py:287} marks the \texttt{mbd} syst group
as ``placeholder'', so no concrete up/down variant configs exist on
disk; the $\pm 5\%$ number is asserted in the note rather than computed.

\paragraph{Recommendation.} Either (a) inject a Photon-4-GeV trigger
efficiency histogram (from \texttt{mbd\_trigger\_efficiency\_study.py}
or the plateau fit in the note) into \texttt{total\_eff} at
\texttt{CalculatePhotonYield.C:1033}, or (b) \emph{document
quantitatively} that the trigger plateau is compatible with unity
within the analysis-range uncertainty and add the residual to the
systematic budget --- \emph{distinct} from the MBD-$\pm 5\%$
systematic.

\subsection{HIGH-2: Note-vs-code trigger-bit mismatch}

\texttt{config\_bdt\_nom.yaml:50}: \texttt{trigger\_used: 30}.
\texttt{PPG12-analysis-note/selection.tex:93}: ``trigger bit 26''.

\noindent Project memory (\texttt{project\_lumi\_list\_provenance.md})
records that ``bit 30 = Photon\_4\_GeV (Map2)''. Joey's
\texttt{get\_luminosity\_182630.C} luminosity mapping has columns
\texttt{Bit\{10,18,22,30\}\{Corr,UC\}}. The analysis note references
bit 26, which is the Photon-4-GeV bit in a \emph{different} map
(likely Map1). If the two trigger maps alias the same physical trigger,
this is a note-update issue; if they do not, then \emph{either} the bit
used for event selection \emph{or} the lumi used for normalization is
wrong.

\paragraph{Recommendation.} Resolve the mapping. If bit 26 and bit 30
are aliases for the same physical trigger across maps, add a one-line
note in \texttt{selection.tex} clarifying the map correspondence. If
they are different, determine which is correct for 60cm-fiducial
lumi-list provenance and fix either the code (\texttt{trigger\_used})
or the note. Cross-check against
\texttt{lumi/60cmLumi\_fromJoey.list} headers.

\subsection{WARN-1: Latent pileup-veto ordering}

\texttt{RecoEffCalculator\_TTreeReader.C} fills the truth-vertex
histograms at lines 1801--1830:
\begin{verbatim}
  if (fabs(vertexz_truth) < vertexcut_truth) {
     h_truth_pT_vertexcut->Fill(particle_Pt, cross_weight);
     if (mbdnorthhit>=1 && mbdsouthhit>=1 && fabs(vertexz) < vertexcut)
        h_truth_pT_vertexcut_mbd_cut->Fill(particle_Pt, cross_weight);
     ...
  }
\end{verbatim}
then applies the MBD-$\sigma_t$ veto at lines 1920--1927:
\begin{verbatim}
  if (mbd_avg_sigma < mbd_avg_sigma_min
      || mbd_avg_sigma > mbd_avg_sigma_max) continue;
\end{verbatim}
The \texttt{continue} skips the reco fills below but the truth
histograms are already set. With the keys not in any on-disk config,
the defaults ($\pm\infty$) make the veto a no-op today.

\paragraph{Recommendation.} Move the MBD-$\sigma_t$ veto before the
truth-denominator fills (or equivalently, apply the same veto to the
truth-fill gate). Even if unused today, the code is a trap for any
future \texttt{mbdrms} systematic.

\section{Reviewer Pass Matrix}

\begin{longtable}{@{}p{3.0cm}p{2.2cm}p{2.2cm}p{2.4cm}p{2.6cm}@{}}
\toprule
Artifact & 2a physics & 2b cosmetics & 2c re-derivation & 3.5 fix-validator \\
\midrule
Data-path cut inventory (Wave 1a) & \ok{PASS} & N/A & N/A & N/A \\
Correction chain inventory (Wave 1b) & \ok{PASS} & N/A & N/A & N/A \\
Truth-fiducial mirror (Wave 1c) & \ok{PASS} & N/A & N/A & N/A \\
Trigger-efficiency verification (Wave 2) & \ok{CONFIRMED} & N/A & N/A & N/A \\
Pileup-veto active/inactive (Wave 2) & \ok{CONFIRMED} & N/A & N/A & N/A \\
NPB/common absorption (Wave 2) & \ok{VERIFIED} & N/A & N/A & N/A \\
\bottomrule
\end{longtable}

Notes: this was a read-only audit. No plots were generated and no
numerical histograms were cited --- so plot-cosmetics (2b) and
numerical re-derivation (2c) are \texttt{N/A}. No code fix was made
in this session (\texttt{3.5} \texttt{N/A}), only recommendations. All
claims in the findings table are backed by three independent agent
reads of the relevant file ranges.

\section{Files Reviewed}

\begin{itemize}
  \item \texttt{efficiencytool/RecoEffCalculator\_TTreeReader.C}
  (cluster loop 1950--2510; truth fills 1801--1830; trigger/vertex/veto
  1493--1927; efficiency fills 2822--2842)
  \item \texttt{efficiencytool/CalculatePhotonYield.C}
  (efficiency application 1027--1043; ABCD 376--602; unfolding 842--1015;
  lumi scaling 1091)
  \item \texttt{efficiencytool/MergeSim.C} (MC pre-merge)
  \item \texttt{efficiencytool/config\_bdt\_nom.yaml}
  \item \texttt{efficiencytool/mbd\_trigger\_efficiency\_study.py}
  (output not consumed)
  \item \texttt{efficiencytool/make\_bdt\_variations.py:275--307}
  (syst taxonomy)
  \item \texttt{plotting/calc\_syst\_bdt.py} (syst groups)
  \item \texttt{anatreemaker/source/CaloAna24.cc} +
  \texttt{.h} (DST preselection)
  \item \texttt{anatreemaker/macro\_maketree/data/ana521/Fun4All\_runDST.C}
  \item \texttt{FunWithxgboost/apply\_BDT.C} (no new cuts)
  \item \texttt{PPG12-analysis-note/selection.tex},
  \texttt{systematics.tex}
\end{itemize}

\section{Recommended Next Steps}

\begin{enumerate}
  \item \textbf{Resolve HIGH-2 first.} Clarify whether
  \texttt{trigger\_used: 30} (code) and ``trigger bit 26'' (note) refer
  to the same physical trigger in different maps, or to different
  triggers. This also constrains the correct 60cm lumi normalization
  (memory flags possible inconsistency with \texttt{Bit30Corr} sums).
  \item \textbf{Fix HIGH-1.} Either inject the Photon-4-GeV L1
  turn-on histogram into \texttt{total\_eff} (preferred, since the
  machinery is in place via \texttt{mbd\_eff\_scale}-style additive
  nuisances) or document the residual explicitly as a systematic
  uncertainty distinct from the MBD $\pm 5\%$. This should be done
  before the next official cross-section release.
  \item \textbf{Close WARN-1.} A three-line reorder in
  \texttt{RecoEffCalculator\_TTreeReader.C} (move the
  \texttt{mbd\_avg\_sigma} veto before line 1801, or duplicate it into
  the truth-fill guard). Low effort; removes the trap.
  \item \textbf{Clean up INFO-1.} Delete
  \texttt{common.e32\_over\_e35\_\{min,max\}} and
  \texttt{common.et1\_\{min,max\}} from the config schema, or wire them
  into \texttt{passes\_common\_shape}.
  \item \textbf{Close the \texttt{mbd} placeholder systematic
  (INFO-2).} Replace the asserted $\pm 5\%$ in
  \texttt{systematics.tex} with an actual
  \texttt{config\_bdt\_mbdeff\_\{up,dn\}.yaml} pair that perturbs the
  \texttt{mbd\_eff\_scale} knob, and let
  \texttt{calc\_syst\_bdt.py} aggregate it like the other systematics.
\end{enumerate}

\end{document}
